\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
\usepackage[utf8]{inputenc}
\usepackage{geometry}
 \geometry{
 a4paper,
 total={170mm,257mm},
 left=20mm,
 top=10mm,
 bottom=5mm,
 }

\title{Soumyakant_Resume}
\author{Soumyakant Priyadarshan}
\date{September 2017}



    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}


% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{2pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
    % END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}


%==== Profile ====%
\begin{center}
	{\Huge \scshape {Soumyakant Priyadarshan}}\\
    Stony Brook,NY $\cdot$ soumyakant.priyadarshan@stonybrook.edu $\cdot$
    (631)636-6925 $\cdot$
    https://www.linkedin.com/in/soumyakant-priyadarshan-1ab87464/\\
\end{center}


%==== Education ====%
\header{Education}
\textbf{Stony Brook University}\hfill Stony Brook,NY\\
PhD candidate, Computer Science \textit{GPA: 3.8/4} \hfill Grad: Dec 23\\
\newline 
Courses: Operating Systems, Artificial Intelligence, Network Programming,
Wireless Networks,System Security, Database Systems, Human Computer
Interaction\\

\textbf{National Institute of Technology}\hfill Rourkela,Odisha,India\\
B. Tech., Computer Science and Engineering \textit{GPA: 7.98/10} \hfill Grad: Jun 13\newline \newline
%==== Skills ====%
\header{SKILLS}
\begin{itemize}
  \itemsep0em
    \item \textbf{Programming Languages}: C, C++, Python, Bash shell scripting,
     SQL/PLSQL, Javascript,JAVA.
	\item \textbf{Databases}: Oracle, MySQL
	\item \textbf{Operating Systems}: Unix, Linux
    \item \textbf{Domain Expertise}: Operating systems, Networking, Systems
    security, Binary instrumentation, Binary analysis, Databases.
\end{itemize}
%==== Experience ====%
\header{RESEARCH WORKS}
\begin{itemize}
\itemsep0em  
  \item \textbf{Area of interest:} System security, Binary instrumentation,
    Binary analysis, Code reuse attacks, Return oriented programming (ROP), Code
    randomization. 
  \item \textbf{Stony Brook Binary Randomizer (SBR) [ACSAC '20]:} SBR is an open
    source tool designed to harden programs against code reuse attacks. SBR
    works can transform binary executables and doesn't rely on source code or
    compilers.  SBR is compatible with stripped COTS binaries. SBR hardens
    binaries by applying code randomization. SBR works well with executables as
    well as shared libraries and has been extensively tested against wide range
    of applications (600 MB of binary code) and low level libraries such as
    glibc, ld.so and libpthread.so. The robustness of SBR makes it an ideal
    candidate to harden and protect an application's entire code space. Unlike
    recent works that heavily rely on relocation information and limit
    themselves only to position independent executables (PIEs), SBR can harden
    both modern PIE binaries as well as non-PIE binaries. SBR has proven to
    offer good protection (84 bits of entropy) with minimal performance overhead
    (2.25\%). 

    \textbf{Link:} http://seclab.cs.sunysb.edu/seclab/sbr/

    \textbf{Publication:} http://seclab.cs.sunysb.edu/seclab/pubs/acsac20.pdf

  \item \textbf{On the Impact of Exception Handling Compatibility on Binary
    Instrumentation [FEAST '20]:} Preserving C++ exception handling and stack
    tracing functionality while hardening binaries can be challenging. This work
    presents a deep dive into the low level implementation of C++ exception
    handling and stack tracing in binary executables and steps necessary to
    ensure the preservation of exception handling functionality in hardened or
    transformed binaries. In this paper, we note that every executable is
    supplied with additional metadata (EH metadata) to support stack tracing and
    C++ exception handling at the runtime. This paper explores how this EH
    metadata can be used to solve various challenges in binary hardening. This
    paper also explores the negative aspect of the EH metadata. It highlights
    how the EH metadata can reduce the effectiveness of binary hardening
    techniques such as code randomization.

    \textbf{Publication:} http://seclab.cs.sunysb.edu/seclab/pubs/feast20.pdf

  \item \textbf{Other notable works:} A study of binary instrumentation
    techniques (http://seclab.cs.sunysb.edu/seclab/pubs/soumyakant\_rpe.pdf)
\end{itemize}

\header{WORK EXPERIENCE}

\textbf{Amdocs Development Center} \hfill Gurgaon,India\\
\textit{Software Engineer} \hfill July 2013 | July 2017\\
\begin{itemize}
\itemsep0em 
  \item Worked in the Data Migration team as End to End Data migration solution
    designer and developer for telecom BSS systems.
  \item Developed ETL(Extract-Transform-Load) software for telecom billing
    systems' data migration projects in TRUE-Move(2013-2014), TRUE-Vision and
    TRUE-Online(2015-2017), NET-Brazil(2014-2015)
  \item Contributed to the development of Data Assurance Tool used for data
    analysis and quality checking.
\end{itemize}
\newpage
\header{COURSE PROJECTS:}
\begin{itemize}
\itemsep0em 
    \item \textbf{Operating system for x86 architecture(64 bit)-[C]}. Features
      include working Shell, timer interrupt(using PIT) and keyboard interrupt,
      walking through PCI to detect AHCI, Paging, Virtual memory, TARFS,
      syscalls(fork, execvpe, wait, waitpid, read, write(stdout),open, close,
      malloc,free, sleep, kill),COW(copy on write) and running
      binaries(ps,cat,ls,kill,cd).\\
    \item \textbf{AI}: \textbf{Decision Tree-[Python]} for mining click-stream
      data collected from Gazelle.com to predict page viewing of a visitor,
      given a set of page views.\\
    \item \textbf{Network Programming-[C]}: \textbf{Trace-route program} along
      with the \textbf{ARP module} to walk around a given ordered list of
      nodes.\\
    \item \textbf{Network Programming-[C]}: \textbf{file transfer application}
      using UDP and added reliability and congestion control using
      acknowledgements and sliding window on top of UDP.\\
    \item \textbf{Android App} to detect device orientation, chop and shake
      gesture using accelerometer.\\
    \item \textbf{System security-[C/C++, javascript]}: Stack Smashing, buffer
      overflow, heap overflow and format string exploits. SQL injection,
      XSS-attack and CSRF attack, system call and library function hooking using
      strace and ptrace. PIN based instrumentation tools.
\end{itemize}


\end{document}


